---
title: "Well Data Report"
subtitle: "Wetland Ecological Integrity Protocol"
author: "Sierra Nevada Network Inventory and Monitoring Program"
format:
  html:
    toc: true
    toc-location: left
---

```{r setup}
library(wetlandwells)
loadWetlandWells() # Load data and functions
```

# Background Information

The data in this report were collected for the Sierra Nevada Network (SIEN) Wetland Ecological Integrity (WEI) monitoring protocol (available from the [IRMA website](https://irma.nps.gov/DataStore/Reference/Profile/2251931)). The network encompasses three park units: Devils Postpile National Monument (DEPO), Sequoia-Kings Canyon National Park (SEKI), and Yosemite National Park (YOSE). The primary components to the SIEN WEI protocol are depth to water in shallow wells, wetland vegetation, and macroinvertebrate communities in fens and wet meadows. This report covers the discrete and continuous depth to water data for the 19 wells in the annual panel where loggers have been deployed. Figure 1 shows a map of the 19 well sites and additional locations where atmospheric pressure data have been collected.

```{r map}
#| fig-cap: "Map of annual panel wells and baro sites in SIEN (DEPO, SEKI, YOSE)"
#| fig-alt: "Yosemite is the northern-most park in the network, in the central Sierra Nevada mountains of California. There are eight wells and four baro sites. Devils Postpile is a small monument located just to the south of Yosemite in the eastern Sierra. There is one well in the park and one baro site just outside the park in Mammoth. Sequoia-Kings Canyon is the southern-most park in the network, in the southern Sierra. There are ten wells and four baro sites. Some wells are installed in wet meadows and some in fens."
siteMap()
```

## Barometric Compensation

Leveloggers measure total pressure, including water column equivalent and barometric pressure from the atmosphere. To determine changes in water level only, barometric pressure must be subtracted from the total pressure.

Barometric pressure data may come from dedicated barologgers or from published weather station data. To ensure best accuracy, Solinst recommends that barometric pressure data should be collected within 20 miles (30 kilometers) and 1000 ft (300 m) elevation of the well levelogger data that they are compensating. This accuracy was not always possible for all of the wells, due to the broad and remote geographic distribution of the wells and gaps in the barometric pressure record due to barologger failure. The closest and best barometric pressure records were chosen for each well. In some cases, multiple records may be used for a single well to ensure coverage of the entire water level record.

Manual barometric compensation follows a simple calculation provided by Solinst (available on the [Solinst website](https://www.solinst.com/products/dataloggers-and-telemetry/3001-levelogger-series/technical-bulletins/barometric-compensation.pdf)).

$Barometric compensated water level (cm) = Raw water column equivalent (cm) + (\frac{Elevation of levelogger (ft) - Elevation of weather station (ft)}{826} \times 30.48(\frac{cm}{ft})) - (Barometric pressure (kPa) \times 10.1972 (\frac{cm}{kPa}))$

# Devils Postpile National Monument(DEPO)

## Location Information

### Well Sites

There is one monitored well in DEPO.

```{r depo_wells}
#| tbl-cap: "Well sites in DEPO"
t <- siteInformation(park = "DEPO", type = "Well")

t |>
  reactable::reactable(
      sortable = TRUE,
      filterable = TRUE,
      compact = TRUE,
      striped = TRUE,
      bordered = TRUE,
      highlight = TRUE,
      resizable = TRUE,
      defaultColDef = reactable::colDef(
        header = function(value) snakecase::to_title_case(value))
      )
```

### Baro Stations

SIEN has never deployed any barologgers in DEPO. Atmospheric pressure data come from the weather station at Mammoth Yosemite Airport (available from [MesoWest website](https://mesowest.utah.edu/cgi-bin/droman/download_api2.cgi?stn=KMMH&hour1=17&min1=34&timetype=LOCAL&unit=0&graph=0)). 

```{r depo_baro}
#| tbl-cap: "Baro sites in DEPO"
siteInformation(park = "DEPO", type = "Baro")
```

## Atmospheric Pressure Data

### Mammoth Yosemite Airport (KMMH)

The weather station record extends from January 2008 to the present with no gaps.

```{r kmmh}
#| fig-cap: "Barometric pressure record for KMMH"
continuousBaroPressure(site = "KMMH")
```

## Water Level Data

### Wet Meadow 409 (Soda Springs)

The well levelogger record is continuous from late August 2014 to September 2024. There are no obvious problems with the record, although the logger was set to collect data once per day instead of once per hour from August 2023 to September 2024. The interval was reset to once per hour during the most recent visit in September 2024. All atmospheric pressure compensation data come from KMMH.

Published data are available [here](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_DEPO_Well-409/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r 409 plot}
#| fig-cap: "Water level record for well 409"
continuousWaterLevel(well = "409")
```

```{r 409 visits}
#| tbl-cap: "Site visit data for well 409"
discreteVisitData(well = "409")
```

```{r 409 loggers}
#| tbl-cap: "Logger deployment data for well 409"
loggerDeployments(well = "409")
```

# Sequoia-Kings Canyon National Park (SEKI)

## Location Information

### Well Sites

There are ten monitored wells in the annual panel at SEKI.

```{r seki_wells}
#| tbl-cap: "Well sites in SEKI"
# siteInformation(park = "SEKI", type = "well")
```

### Baro Stations

SIEN has deployed three barologgers in SEKI. Additional atmospheric pressure data come from the weather station at State Lakes (available from [CDEC website](https://cdec.water.ca.gov/dynamicapp/staMeta?station_id=STL)). 

```{r seki_baro}
#| tbl-cap: "Baro sites in SEKI"
# siteInformation(park = "SEKI", type = "baro")
```

## Atmospheric Pressure Data

### Baro 306 (Shorty's Meadow)

The record begins in XXXX 2014. There is a gap from XXXX 2015 to XXX 2016 due to ________________. A new barologger was deployed in XXXX 2016. The barologger was successfully downloaded in August 2020. The same barologger was recovered during the next site visit in September 2024 but was unable to be downloaded, likely due to a dead battery. The barologger is currently being shipped to the manufacturer for troubleshooting. A replacement barologger was deployed in September 2024 and is currently logging.

```{r 306b}
#| fig-cap: "Barometric pressure record for 306"
# continuousBaroPressure(site = "306")
```

### Baro 315 (Lake South America)

The record begins in XXXX 2014. A new barologger was deployed in XXXX 2016. The barologger was successfully downloaded in August 2020, which was the last time the site was visited. The barologger is currently logging.

```{r 315b}
#| fig-cap: "Barometric pressure record for 315"
# continuousBaroPressure(site = "315")
```

### Baro 308 (Lower Dusy Basin)

No atmospheric pressure data have been collected yet from this site. A levelogger was deployed as a barologger by mistake in 20__. A barologger was deployed there in ______. The site has not been revisited since then, so the barologger has not yet been downloaded. Presumably, it is currently collecting data.

```{r 308b, eval = FALSE}
#| fig-cap: "Barometric pressure record for 308"
# continuousBaroPressure(site = "308")
```

### State Lakes (STL CDEQ)

This is a relatively new weather station installed by the Army Corps of Engineers near State Lakes. The record extends from October 2023 to the present with no gaps.

```{r STL}
#| fig-cap: "Barometric pressure record for STL"
# continuousBaroPressure(site = "STL")
```

## Water Level Data

### Wet Meadow 308 (Lower Dusy Basin)

```{r 308}
#| fig-cap: "Water level record for well 308"
# continuousWaterLevel(well = "308")
```

### Fen 305 (Shorty's Meadow)

```{r 305}
#| fig-cap: "Water level record for well 305"
# continuousWaterLevel(well = "305")
```

### Wet Meadow 306 (Shorty's Meadow)

```{r 306}
#| fig-cap: "Water level record for well 306"
# continuousWaterLevel(well = "306")
```

### Fen 319 (Silliman)

```{r 319}
#| fig-cap: "Water level record for well 319"
# continuousWaterLevel(well = "319")
```

### Wet Meadow 320 (Silliman)

```{r 320}
#| fig-cap: "Water level record for well 320"
# continuousWaterLevel(well = "320")
```

### Wet Meadow 310 (Windy Gap)

```{r 310}
#| fig-cap: "Water level record for well 310"
# continuousWaterLevel(well = "310")
```

### Fen 345 (Hay Meadow)

```{r 345}
#| fig-cap: "Water level record for well 345"
# continuousWaterLevel(well = "345")
```

### Wet Meadow 348 (Hay Meadow)

```{r 348}
#| fig-cap: "Water level record for well 348"
# continuousWaterLevel(well = "348")
```

### Wet Meadow 314 (Lake South America)

```{r 314}
#| fig-cap: "Water level record for well 314"
# continuousWaterLevel(well = "314")
```

### Fen 315 (Lake South America)

```{r 315}
#| fig-cap: "Water level record for well 315"
# continuousWaterLevel(well = "315")
```

# Yosemite National Park (YOSE)

## Location Information

### Well Sites

There are eight monitored wells in the annual panel at YOSE.

```{r yose_wells}
#| tbl-cap: "Well sites in YOSE"
# siteInformation(park = "YOSE", type = "well")
```

### Baro Stations

There are three primary barologgers operated and maintained by park staff at YOSE. There is also one barologger operated and maintained by network staff at SIEN. 

```{r yose_baro}
#| tbl-cap: "Baro sites in YOSE"
# siteInformation(park = "YOSE", type = "baro")
```

## Atmospheric Pressure Data

### Bug Camp (BUGL)

```{r bugl}
#| fig-cap: "Barometric pressure record for BUGL"
# continuousBaroPressure(site = "BUGL")
```

### Illilouette Creek (ILLI)

```{r illi}
#| fig-cap: "Barometric pressure record for ILLI"
# continuousBaroPressure(site = "ILLI")
```

### Above High Sierra Camp (AHSC)

```{r ahsc}
#| fig-cap: "Barometric pressure record for AHSC"
# continuousBaroPressure(site = "AHSC")
```

### Baro 214 (Kendrick Creek)

No atmospheric pressure data have been collected yet from this site. A levelogger was deployed as a barologger by mistake in 20__. A barologger was deployed there in ______. The site has not been revisited since then, so the barologger has not yet been downloaded. Presumably, it is currently collecting data.

Unfortunately, the logger deployed from X to Y was a levelogger and not a barologger. The logger exhibited wild fluctuations during the summer months that may have been due to the logger sensitivity being designed for underwater deployment or to the logger being deployed in direct sunlight, which can overheat the logger and introduce error.

```{r 214b, eval = FALSE}
#| fig-cap: "Barometric pressure record for 214"
# continuousBaroPressure(site = "214")
```

## Water Level Data

### Wet Meadow 214 (Kendrick Creek)

```{r 214}
#| fig-cap: "Water level record for well 214"
# continuousWaterLevel(well = "214")
```

### Wet Meadow 224 (Bridalveil)

```{r 224}
#| fig-cap: "Water level record for well 224"
# continuousWaterLevel(well = "224")
```

### Wet Meadow 301 (Echo Creek)

```{r 301}
#| fig-cap: "Water level record for well 301"
# continuousWaterLevel(well = "301")
```

### Fen 327 (Echo Creek)

```{r 327}
#| fig-cap: "Water level record for well 327"
# continuousWaterLevel(well = "327")
```

### Wet Meadow 313 (Budd Creek)

```{r 313}
#| fig-cap: "Water level record for well 313"
# continuousWaterLevel(well = "313")
```

### Fen 328 (Bridalveil)

```{r 328}
#| fig-cap: "Water level record for well 328"
# continuousWaterLevel(well = "328")
```

### Wet Meadow 322 (Porcupine Flat)

```{r 322}
#| fig-cap: "Water level record for well 322"
# continuousWaterLevel(well = "322")
```

### Fen 323 (Porcupine Flat)

```{r 323}
#| fig-cap: "Water level record for well 323"
# continuousWaterLevel(well = "323")
```
