---
title: "Well Data Report"
subtitle: |
    | Wetland Ecological Integrity Protocol
    | Sierra Nevada Network I&M Program
author: "Jennifer Bailard"
date: today
execute: 
  echo: false
format:
  html:
    embed-resources: true
    toc: true
    toc-location: left
tbl-cap-location: top
---

```{r setup}
library(wetlandwells)
loadWetlandWells() # Load data and functions
```

# Background Information

The data in this report were collected for the Sierra Nevada Network (SIEN) Wetland Ecological Integrity (WEI) monitoring protocol (available from the [IRMA website](https://irma.nps.gov/DataStore/Reference/Profile/2251931)). The network encompasses three park units: Devils Postpile National Monument (DEPO), Sequoia-Kings Canyon National Park (SEKI), and Yosemite National Park (YOSE). The primary components to the SIEN WEI protocol are depth to water in shallow wells, wetland vegetation, and macroinvertebrate communities in fens and wet meadows. This report covers the discrete and continuous depth to water data for the 19 wells in the annual panel where loggers have been deployed. Figure 1 shows a map of the 19 well sites and additional locations where atmospheric pressure data have been collected.

```{r, warning = FALSE}
#| label: fig-sitemap
#| fig-cap: "Map of annual panel wells and baro sites in SIEN (DEPO, SEKI, YOSE)"
#| fig-alt: "Yosemite is the northern-most park in the network, in the central Sierra Nevada mountains of California. There are eight wells and four baro sites. Devils Postpile is a small monument located just to the south of Yosemite in the eastern Sierra. There is one well in the park and one baro site just outside the park in Mammoth. Sequoia-Kings Canyon is the southern-most park in the network, in the southern Sierra. There are ten wells and four baro sites. Some wells are installed in wet meadows and some in fens."
siteMap()
```

## Barometric Compensation

Leveloggers measure total pressure, including water column equivalent and barometric pressure from the atmosphere. To determine changes in water level only, barometric pressure must be subtracted from the total pressure.

Barometric pressure data may come from dedicated barologgers or from published weather station data. To ensure best accuracy, Solinst recommends that barometric pressure data should be collected within 20 miles (30 kilometers) and 1000 ft (300 m) elevation of the well levelogger data that they are compensating. This accuracy was not always possible for all of the wells, due to the broad and remote geographic distribution of the wells and gaps in the barometric pressure record due to barologger failure. The closest and best barometric pressure records were chosen for each well. In some cases, multiple records may be used for a single well to ensure coverage of the entire water level record.

Manual barometric compensation follows a simple calculation provided by Solinst (available on the [Solinst website](https://www.solinst.com/products/dataloggers-and-telemetry/3001-levelogger-series/technical-bulletins/barometric-compensation.pdf)).

| Barometric compensated water level $(cm)$ $=$
|
|       Raw water column equivalent $(cm)$ $+$
|
|       $($Elevation of levelogger $(ft)$ $-$ Elevation of weather station $(ft))$ / $826 \times 30.48(\frac{cm}{ft})$ $-$
|
|       Barometric pressure $(kPa)$ $\times$ $10.1972 (\frac{cm}{kPa})$

# Devils Postpile National Monument(DEPO)

## Location Information

### Well Sites

There is one monitored well in DEPO.

```{r}
#| label: tbl-depo_wells
#| tbl-cap: "Well sites in DEPO"
siteInformationWellReactable(park = "DEPO")
```

### Baro Stations

SIEN has never deployed any barologgers in DEPO. Atmospheric pressure data come from the weather station at Mammoth Yosemite Airport. 

```{r}
#| label: tbl-depo_baro
#| tbl-cap: "Baro sites in DEPO"
siteInformationBaroReactable(park = "DEPO")
```

## Atmospheric Pressure Data

### Mammoth Yosemite Airport (KMMH)

The weather station record extends from January 2008 to the present with no gaps.

Continuous barometric data are available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_DEPO_MesoWest-KMMH/DataSet/Atmos%20Pres/Baro/Interval/AllData). Original data are available to view and download from [MesoWest](https://mesowest.utah.edu/cgi-bin/droman/download_api2.cgi?stn=KMMH&hour1=17&min1=34&timetype=LOCAL&unit=0&graph=0).


```{r}
#| label: fig-kmmh
#| fig-cap: "Barometric pressure record for KMMH"
continuousBaroPressure(site = "KMMH")
```

## Water Level Data

### Wet Meadow 409 (Soda Springs)

*Note: This well was originally numbered 409. It was renumbered to 337 in 2016. However, it is still usually referred to as 409.*

The record begins in late August 2014 and is continuous through September 2024. The logger was accidentally set to collect data once per day instead of once per hour from August 2023 to September 2024. The interval was reset to once per hour during the most recent visit in September 2024. All atmospheric pressure compensation data come from KMMH.

There is some logger data from July 2009 to September 2010 and from October 2011 to December 2012. The logger was set to collect data every 15 minutes during both of these deployments, which caused the memory to become full in a little over a year. Since the site was only visited every two years, this led to gaps in the record between visits. The logger was changed to record once per hour in August 2014. Additionally, there are no documented depth to water measurements during this period. Without field measurements to which to tie the logger record, the offset applied to the data is only a guess and does not necessarily reflect actual conditions in the well with confidence.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_DEPO_Well-409/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-409plot
#| fig-cap: "Water level record for well 409"
continuousWaterLevel(well = "409")
```

```{r}
#| label: tbl-409visits
#| tbl-cap: "Site visit data for well 409"
discreteVisitDataReactable(well = "409")
```

```{r}
#| label: tbl-409loggers
#| tbl-cap: "Logger deployment data for well 409"
loggerWellDeploymentsReactable(well = "409")
```

# Sequoia-Kings Canyon National Park (SEKI)

## Location Information

### Well Sites

There are ten monitored wells in the annual panel at SEKI.

```{r}
#| label: tbl-seki_wells
#| tbl-cap: "Well sites in SEKI"
siteInformationWellReactable(park = "SEKI")
```

### Baro Stations

SIEN has deployed three barologgers in SEKI. Additional atmospheric pressure data come from the weather station at State Lakes. 

```{r}
#| label: tbl-seki_baro
#| tbl-cap: "Baro sites in SEKI"
siteInformationBaroReactable(park = "SEKI")
```

## Atmospheric Pressure Data

### Baro 306 (Shorty's Meadow)

The record begins in July 2014. There is a gap from June 2015 to June 2016 because no barologger was deployed. The same barologger was deployed again in July 2016. The barologger was successfully downloaded in August 2020. The same barologger was recovered during the next site visit in September 2024 but was unable to be downloaded, likely due to a dead battery. The barologger is currently being shipped to the manufacturer for troubleshooting. A replacement barologger was deployed in September 2024 and is currently logging.

Continuous barometric data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_SEKI-02_Well-306/DataSet/Atmos%20Pres/Baro/Interval/AllData)

```{r}
#| label: fig-306bplot
#| fig-cap: "Barometric pressure record for baro site 306"
continuousBaroPressure(site = "306")
```

```{r}
#| label: tbl-306bloggers
#| tbl-cap: "Logger deployment data for baro site 306"
loggerBaroDeploymentsReactable(site = "306")
```

### Baro 315 (Lake South America)

The record begins in late August 2014 and is continuous through early September 2020, which is the last time the barologger was downloaded. While the two well leveloggers at the site were downloaded in 2021 and 2023, the barologger was not downloaded during these visits. The same barologger is currently deployed at the site. If the logger memory was not cleared during the last visit, then the logger memory is probably full, and the logger may not be recording data. The logger is also reaching end of its battery life.

Continuous barometric data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_SEKI-06_Well-315/DataSet/Atmos%20Pres/Baro/Interval/AllData)

```{r}
#| label: fig-315bplot
#| fig-cap: "Barometric pressure record for baro site 315"
continuousBaroPressure(site = "315")
```

```{r}
#| label: tbl-315bloggers
#| tbl-cap: "Logger deployment data for baro site 315"
loggerBaroDeploymentsReactable(site = "315")
```

### Baro 308 (Lower Dusy Basin)

No useable atmospheric pressure data have been collected yet from this site. A Gold model barologger was deployed in September 2016. This logger was  programmed to collect baro data in units of water equivalent instead of pressure. This logger exhibited very large and suspect fluctuations for most of the record. Aside from the programming problem, communications with Solinst suggest problems could also have been due to the age of the logger or deployment in direct sunlight. A new barologger was deployed in September 2023. The site has not been revisited since then, so the new barologger has not yet been downloaded.

Continuous barometric data are available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_SEKI-01_Well-308/DataSet/Atmos%20Pres/Baro/Interval/AllData)

```{r, eval = FALSE}
#| label: fig-308bplot
#| fig-cap: "Barometric pressure record for baro site 308"
continuousBaroPressure(site = "308")
```

```{r}
#| label: tbl-308bloggers
#| tbl-cap: "Logger deployment data for baro site 308"
loggerBaroDeploymentsReactable(site = "308")
```

### State Lakes (STL CDEC)

This is a relatively new weather station installed by the Army Corps of Engineers near State Lakes. The record extends from October 2023 to the present with no gaps.

Continuous barometric data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_SEKI_CDEC-STL/DataSet/Atmos%20Pres/Baro/Interval/AllData). Original data are available to view and download from [CDEC](https://cdec.water.ca.gov/dynamicapp/staMeta?station_id=STL).

```{r}
#| label: fig-STLplot
#| fig-cap: "Barometric pressure record for STL"
continuousBaroPressure(site = "STL")
```

## Water Level Data

The earliest baro record begins in mid July 2014 at baro site 306 and runs until late July 2020. The baro record from baro site 315 begins in late August 2014 and runs until early September 2020. All sites in SEKI use one of these two records for barometric compensation during this time.

Between early September 2020 and early October 2023, there is no baro logger record from within SEKI. The baro record from Bug Camp in YOSE was used for barometric compensation during this time. Use of this record is not ideal due to how far away it is located, but it is the closest and best available record unless other baro records are discovered. Beginning in early October 2023, the weather station at State Lakes came online.

### Wet Meadow 308 (Lower Dusy Basin)

The record begins in July 2015 and is continuous through September 2023. There are periods in late summer and fall of 2016, 2020, and 2021 when the water level in the well dropped below the suspended logger. The logger was left in place during the last visit in September 2023 and is currently collecting data.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_SEKI-01_Well-308/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-308plot
#| fig-cap: "Water level record for well 308"
continuousWaterLevel(well = "308")
```

```{r}
#| label: tbl-308visits
#| tbl-cap: "Site visit data for well 308"
discreteVisitDataReactable(well = "308")
```

```{r}
#| label: tbl-308loggers
#| tbl-cap: "Logger deployment data for well 308"
loggerWellDeploymentsReactable(well = "308")
```

### Fen 305 (Shorty's Meadow)

The record begins in late September 2017 and is continuous through early March 2023, when the logger memory became full. Since the logger was not programmed to overwrite older data, it stopped recording at this time. A new logger was deployed during the last visit in September 2024.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_SEKI-02_Well-305/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-305plot
#| fig-cap: "Water level record for well 305"
continuousWaterLevel(well = "305")
```

```{r}
#| label: tbl-305visits
#| tbl-cap: "Site visit data for well 305"
discreteVisitDataReactable(well = "305")
```

```{r}
#| label: tbl-305loggers
#| tbl-cap: "Logger deployment data for well 305"
loggerWellDeploymentsReactable(well = "305")
```

### Wet Meadow 306 (Shorty's Meadow)

The record begins in July 2014. There is a gap from June 2015 to June 2016 because no logger was deployed. The same logger was deployed again in late June 2016. The logger was successfully downloaded in late July 2021. The same logger was recovered during the next site visit in September 2024 but was unable to be downloaded, likely due to a dead battery. The logger is currently being shipped to the manufacturer for troubleshooting. A new logger was deployed in September 2024 and is currently logging.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_SEKI-02_Well-306/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-306plot
#| fig-cap: "Water level record for well 306"
continuousWaterLevel(well = "306")
```

```{r}
#| label: tbl-306visits
#| tbl-cap: "Site visit data for well 306"
discreteVisitDataReactable(well = "306")
```

```{r}
#| label: tbl-306loggers
#| tbl-cap: "Logger deployment data for well 306"
loggerWellDeploymentsReactable(well = "306")
```

### Fen 319 (Silliman)

The record begins in June 2014 and is continuous through the end of December 2022. There are some periods in late summer and fall of 2021 and 2022 when the water level in the well dropped below the suspended logger. In January 2023, the well logger began exhibiting large drops and jumps, and the data became suspect. The same logger is currently deployed and is likely nearing a full memory and the end of its battery life. The logger should be replaced during the next visit.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_SEKI-03_Well-319/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-319plot
#| fig-cap: "Water level record for well 319"
continuousWaterLevel(well = "319")
```

```{r}
#| label: tbl-319visits
#| tbl-cap: "Site visit data for well 319"
discreteVisitDataReactable(well = "319")
```

```{r}
#| label: tbl-319loggers
#| tbl-cap: "Logger deployment data for well 319"
loggerWellDeploymentsReactable(well = "319")
```

### Wet Meadow 320 (Silliman)

The record begins in June 2016 and is continuous through mid January 2023. There are some periods in late summer and fall of 2021 and 2022 when the water level in the well dropped below the suspended logger. In January 2023, the memory became full and the logger stopped recording data, since it was not set to overwrite data. The logger was left in place during the last visit in August 2023. If the logger memory was not cleared, then the logger is  not collecting data right now due to a full memory and is also likely reaching end of its battery life.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_SEKI-03_Well-320/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-320plot
#| fig-cap: "Water level record for well 320"
continuousWaterLevel(well = "320")
```

```{r}
#| label: tbl-320visits
#| tbl-cap: "Site visit data for well 320"
discreteVisitDataReactable(well = "320")
```

```{r}
#| label: tbl-320loggers
#| tbl-cap: "Logger deployment data for well 320"
loggerWellDeploymentsReactable(well = "320")
```

### Wet Meadow 310 (Windy Gap)

The record begins in August 2014. There was a short period in late summer 2015 when the water level in the well dropped below the suspended logger. The logger was removed from the well in June 2016 because it could not be downloaded in the field. However, the logger was successfully downloaded in the office. A new logger was not deployed in the well until July 2017. This logger was last downloaded during the last visit in August 2021. There are some periods in summer 2021 when the water level in the well dropped below the suspended logger. The same logger is currently deployed and is likely nearing a full memory and the end of its battery life. The logger should be replaced during the next visit.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_SEKI-04_Well-310/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-310plot
#| fig-cap: "Water level record for well 310"
continuousWaterLevel(well = "310")
```

```{r}
#| label: tbl-310visits
#| tbl-cap: "Site visit data for well 310"
discreteVisitDataReactable(well = "310")
```

```{r}
#| label: tbl-310loggers
#| tbl-cap: "Logger deployment data for well 310"
loggerWellDeploymentsReactable(well = "310")
```

### Fen 345 (Hay Meadow)

The record begins in July 2014. The logger was removed from the well in May 2015 because it could not be downloaded in the field. While the logger was later successfully downloaded in the office, it had been set to record in units of pressure (psi) instead of water column equivalent (cm) during its deployment. A new logger was deployed during the next visit in July 2016. The water level was close to the ground surface for most of the record until summer 2021, when the water level dropped from July to September. Beginning in December 2021, the logger readings became erratic. Except for June and July 2022, there were large fluctuations in the record, and the fluctuations appeared inconsistent with the diurnal and longer-term signals in the barometric record. The logger was removed during the last visit in July 2023 because it could not be downloaded in the field. However, the logger was successfully downloaded in the office. A new logger was deployed during that visit and is currently logging.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_SEKI-05_Well-345/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-345plot
#| fig-cap: "Water level record for well 345"
continuousWaterLevel(well = "345")
```

```{r}
#| label: tbl-345visits
#| tbl-cap: "Site visit data for well 345"
discreteVisitDataReactable(well = "345")
```

```{r}
#| label: tbl-345loggers
#| tbl-cap: "Logger deployment data for well 345"
loggerWellDeploymentsReactable(well = "345")
```

### Wet Meadow 348 (Hay Meadow)

The record begins in July 2016 and is continuous through July 2023. There is a period in September 2021 when the water level in the well likely dropped below the suspended logger. Beginning in fall 2022, the record began to exhibit large fluctuations and drift upward above the level of the top of the well casing. These data are suspect and may not be usable. The logger was removed during the last visit in July 2023 because it could not be downloaded in the field. However, the logger was successfully downloaded in the office. A new logger was deployed during that visit and is currently logging.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_SEKI-05_Well-348/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-348plot
#| fig-cap: "Water level record for well 348."
continuousWaterLevel(well = "348")
```

```{r}
#| label: tbl-348visits
#| tbl-cap: "Site visit data for well 348"
discreteVisitDataReactable(well = "348")
```

```{r}
#| label: tbl-348loggers
#| tbl-cap: "Logger deployment data for well 348"
loggerWellDeploymentsReactable(well = "348")
```

### Wet Meadow 314 (Lake South America)

The record begins in August 2015. The logger deployed in August 2015 (previously deployed at well 345 in SEKI) was set to record in units of pressure (psi) instead of water column equivalent (cm) during its entire deployment. This logger could not be downloaded in August 2020. The record for this logger ends in April 2019. It is unclear if some data were later successfully downloaded in the office, or if there was an undocumented visit to the site in April 2019. A new logger was deployed in September 2020, but there is no information on this deployment. A new logger was again deployed in September 2023 and is currently logging.

There are a couple of concerns with this record. From November 2020 to May 2021, the record drifted nearly half a meter above the ground surface, well above the level of the top of the well casing. These data are suspect and may not be usable. Additionally, throughout the record, the logger exhibited large diurnal fluctuations during the summer, starting around the onset of snowmelt and tapering off in the fall. It is unclear what is causing these fluctuations or if they reflect actual conditions in the well.

Lake South America is the highest elevation annual panel site monitored for this protocol. Factors in the local environment, such as prolonged cold, ice, or snow, may be affecting the deployed loggers and the quality of the record.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_SEKI-06_Well-314/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-314plot
#| fig-cap: "Water level record for well 314"
continuousWaterLevel(well = "314")
```

```{r}
#| label: tbl-314visits
#| tbl-cap: "Site visit data for well 314"
discreteVisitDataReactable(well = "314")
```

```{r}
#| label: tbl-314loggers
#| tbl-cap: "Logger deployment data for well 314"
loggerWellDeploymentsReactable(well = "314")
```

### Fen 315 (Lake South America)

The record begins in September 2016 and is continuous through early September 2023. The same logger has been deployed for the entire period and is currently logging since the last visit in September 2023. This logger may be nearing the end of its battery life and should be replaced during the next visit.

There were two periods where the record spiked far higher than the level of the top of the well casing. The first occurred in May and June 2017, and the second occurred in May and June 2023. These data may be due to effects on the logger from snowmelt during high snowpack years.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_SEKI-06_Well-315/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-315plot
#| fig-cap: "Water level record for well 315"
continuousWaterLevel(well = "315")
```

```{r}
#| label: tbl-315visits
#| tbl-cap: "Site visit data for well 315"
discreteVisitDataReactable(well = "315")
```

```{r}
#| label: tbl-315loggers
#| tbl-cap: "Logger deployment data for well 315"
loggerWellDeploymentsReactable(well = "315")
```

# Yosemite National Park (YOSE)

## Location Information

### Well Sites

There are eight monitored wells in the annual panel at YOSE.

```{r}
#| label: tbl-yose_wells
#| tbl-cap: "Well sites in YOSE"
siteInformationWellReactable(park = "YOSE")
```

### Baro Stations

There are three primary barologgers operated and maintained by park staff at YOSE. There is also one barologger operated and maintained by network staff at SIEN. 

```{r}
#| label: tbl-yose_baro
#| tbl-cap: "Baro sites in YOSE"
siteInformationBaroReactable(park = "YOSE")
```

## Atmospheric Pressure Data

### Bug Camp (BUGL)

The record begins in August 2012. There is a gap from early August 2013 to June 2014. There is another gap from late August 2019 to late August 2020. The barologger was most recently downloaded during the last visit in August 2024.

The record appeared to be slightly vertically offset during the first deployment from August 2012 to August 2013, higher than all the other years. A correction (-0.70 kPa) was applied to the data during this period to be consistent with the other years.

The record also appeared to be slightly horizontally offset between early September 2018 and late August 2019, by about 7 hours compared to weather station data from KMMH. The file for this deployment year may have accidentally been flagged as UTC during upload. A correction was applied to shift the record to the correct time zone.

From late November 2018 to late August 2019, the record exhibited numerous large offsets, during some periods on a daily basis. It is unclear what may have been causing the barologger to malfunction. Alternative records from other sites were used for barometric compensation during this time.

Because this barologger is maintained by YOSE, there is no logger deployment information. Continuous barometric data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_YOSE_TUOL_BUGL/DataSet/Absolute%20Pressure/Baro/Interval/AllData).

```{r}
#| label: fig-BUGLplot
#| fig-cap: "Barometric pressure record for Bug Camp"
continuousBaroPressure(site = "BUGL")
```

### Illilouette Creek (ILLI)

The record begins in October 2015 and is continuous through September 2023.

The record appeared to be slightly vertically offset between September 2016 and October 2017, lower than all the other years. A correction (0.65 kPa) was applied to the data during this period to be consistent with the other years. Additionally, there were unusually large diurnal fluctuations during this same period. It is unclear what may have been causing the barologger to malfunction. Alternative records from other sites were used for barometric compensation during this time.

Because this barologger is maintained by YOSE, there is no logger deployment information. Continuous barometric data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_YOSE_MERC_ILLI/DataSet/Atmos%20Pres/Baro/Interval/AllData).

```{r}
#| label: fig-ILLIplot
#| fig-cap: "Barometric pressure record for Illilouette Creek"
continuousBaroPressure(site = "ILLI")
```

### Merced River Above High Sierra Camp (AHSC)

The record begins in September 2017. There is a gap from October 2020 to August 2022. The barologger was most recently downloaded during the last visit in August 2024.

The record appeared to be slightly horizontally offset between early September 2018 and late August 2019, by about 7 hours compared to the weather station at KMMH. The file for this deployment year may have accidentally been flagged as UTC during upload. A correction was applied to shift the record to the correct time zone.

The record also appears to be slightly horizontally offset between early October 2023 and early August 2024, by about 7 hours compared to the weather station at KMMH. This was also probably due to incorrect time zone flagging during upload. A correction was applied to shift the record to a consistent time zone.

During February 2019, the record exhibited noticeably larger than normal diurnal fluctuations, and possibly at other periods during the deployment from September 2018 to August 2019. Alternative records from other sites were used for barometric compensation during this time.

Because this barologger is maintained by YOSE, there is no logger deployment information. Continuous barometric data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_YOSE_MERC_AHSC/DataSet/Atmos%20Pres/Baro/Interval/AllData).

```{r}
#| label: fig-AHSCplot
#| fig-cap: "Barometric pressure record for Above High Sierra Camp"
continuousBaroPressure(site = "AHSC")
```

### Baro 214 (Kendrick Creek)

The record begins in June 2015. However, since the file exports contain units of water column equivalent (m) instead of pressure (psi or kPa), it appears that a levelogger was deployed instead of a barologger by mistake. Additionally, Gold model leveloggers applied a sea level normalization to the data. Consequently, a correction (-29.1 kPa) was applied to the data collected by this logger to approximate the actual atmospheric pressure at the elevation of the site.

From September 2018 to early September 2023, the record exhibited wild fluctuations during the summer months that may have been due to the logger sensitivity being designed for underwater deployment or to the logger being deployed in direct sunlight, which can overheat the logger and introduce error.

A replacement barologger was deployed in early September 2023 and is currently logging. The site has not been visited again since then, so this new logger has not yet been downloaded.

Continuous barometric data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_YOSE-01_Well-214/DataSet/Atmos%20Pres/Baro/Interval/AllData).

```{r}
#| label: fig-214bplot
#| fig-cap: "Barometric pressure record for baro site 214"
continuousBaroPressure(site = "214")
```

```{r}
#| label: tbl-214bloggers
#| tbl-cap: "Logger deployment data for baro site 214"
loggerBaroDeploymentsReactable(site = "214")
```

## Water Level Data

The earliest baro record begins in late July 2012 at BUGL and runs until late August 2024, with gaps or unusable data from August 2013 to June 2014 and from December 2018 to late August 2020. This second period can be filled with data from AHSC.

The baro record at AHSC begins in September 2017 and runs until early August 2024, with a some questionable data around February 2019 and a gap from October 2020 to late August 2022. The first period can be filled with data from ILLI and the second with data from BUGL.

The baro record at ILLI begins in October 2015 and runs until late September 2023, with a unusable data from early September 2016 to October 2017. This period can be filled with data from BUGL.

The baro record at 214 begins in late June 2015 and runs until late September 2018. This record has had some problems (described previously), so it is not being used for barometric compensation at this time. Once the new logger is downloaded, this site may provide usable data. 

Most sites in YOSE primarily use the record from BUGL for barometric compensation, with some sites prioritizing AHSC or ILLI depending on proximity.

### Wet Meadow 214 (Kendrick Creek)

The record begins in July 2015 and is continuous through early September 2023. The current logger has been deployed since July 2015 (originally at well 308 in SEKI) and has been logging since the last visit in September 2023. This logger may be nearing the end of its battery life and should be replaced during the next visit.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_YOSE-01_Well-214/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-214plot
#| fig-cap: "Water level record for well 214"
continuousWaterLevel(well = "214")
```

```{r}
#| label: tbl-214visits
#| tbl-cap: "Site visit data for well 214"
discreteVisitDataReactable(well = "214")
```

```{r}
#| label: tbl-214loggers
#| tbl-cap: "Logger deployment data for well 214"
loggerWellDeploymentsReactable(well = "214")
```

### Wet Meadow 224 (Bridalveil)

The record begins in late August 2015 and is continuous through October 2022. The well was dry when it was first installed, and there is a period in late summer and early fall 2015 when the water level in the well was below the suspended logger. A new logger was deployed during the last visit in October 2022 and is currently logging.

** Was this the well that was not found in 2023? Double-check.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_YOSE-03_Well-224/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-224plot
#| fig-cap: "Water level record for well 224"
continuousWaterLevel(well = "224")
```

```{r}
#| label: tbl-224visits
#| tbl-cap: "Site visit data for well 224"
discreteVisitDataReactable(well = "224")
```

```{r}
#| label: tbl-224loggers
#| tbl-cap: "Logger deployment data for well 224"
loggerWellDeploymentsReactable(well = "224")
```

### Wet Meadow 301 (Echo Creek)

The record begins in July 2016 and is continuous through early November 2020. At this time, the logger began to malfunction and then stopped recording entirely. The logger was replaced in September 2023. The current logger has been deployed since August 2015 (originally at well 224 in YOSE) and has been logging since the last visit in September 2023. This logger may be nearing the end of its battery life and should be replaced during the next visit.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_YOSE-04_Well-301/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-301plot
#| fig-cap: "Water level record for well 301"
continuousWaterLevel(well = "301")
```

```{r}
#| label: tbl-301visits
#| tbl-cap: "Site visit data for well 301"
discreteVisitDataReactable(well = "301")
```

```{r}
#| label: tbl-301loggers
#| tbl-cap: "Logger deployment data for well 301"
loggerWellDeploymentsReactable(well = "301")
```

### Fen 327 (Echo Creek)

*Note: This well was originally numbered 225. It was renumbered to 327 in 2016.*

The record begins in late July 2016 and runs through August 2022. A logger had been deployed during the first visit in July 2015; however, it had not been set to start recording data. The logger was launched during the next visit in July 2016. The logger could not be downloaded during the last visit in August 2023. However, the crew did not have a spare logger, so the same logger was left in place. The logger probably has a dead battery and is not collecting data. It should be replaced during the next visit.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_YOSE-04_Well-327/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-327plot
#| fig-cap: "Water level record for well 327"
continuousWaterLevel(well = "327")
```

```{r}
#| label: tbl-327visits
#| tbl-cap: "Site visit data for well 327"
discreteVisitDataReactable(well = "327")
```

```{r}
#| label: tbl-327loggers
#| tbl-cap: "Logger deployment data for well 327"
loggerWellDeploymentsReactable(well = "327")
```

### Wet Meadow 313 (Budd Creek)

The record begins in August 2016 and is continuous through September 2023. A logger had been deployed during the first visit in July 2015; however, the crew observed during the next visit in August 2016 that the well and logger had been pulled out of the ground, possibly due to coyotes. Based on the temperature record from the logger, this happened within a week of the well installation, so the first year of data are unusable. There are periods in late summer and fall of 2016, 2018, 2019, 2020, 2021, and 2022 when the water level in the well dropped below the suspended logger. A new logger was deployed in August 2022 and is currently logging.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_YOSE-06_Well-313/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-313plot
#| fig-cap: "Water level record for well 313"
continuousWaterLevel(well = "313")
```

```{r}
#| label: tbl-313visits
#| tbl-cap: "Site visit data for well 313"
discreteVisitDataReactable(well = "313")
```

```{r}
#| label: tbl-313loggers
#| tbl-cap: "Logger deployment data for well 313"
loggerWellDeploymentsReactable(well = "313")
```

### Fen 328 (Bridalveil)

The record begins in late August 2016 and is continuous through late September 2023. There is a period in winter 2021 when the water level in the well dropped below the suspended logger. A new logger was deployed during the last visit in September 2023 and is currently logging.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_YOSE-07_Well-328/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-328plot
#| fig-cap: "Water level record for well 328"
continuousWaterLevel(well = "328")
```

```{r}
#| label: tbl-328visits
#| tbl-cap: "Site visit data for well 328"
discreteVisitDataReactable(well = "328")
```

```{r}
#| label: tbl-328loggers
#| tbl-cap: "Logger deployment data for well 328"
loggerWellDeploymentsReactable(well = "328")
```

### Wet Meadow 322 (Porcupine Flat)

The record begins in late August 2016. There are periods in late summer and fall of 2016, 2018, 2019, 2020, and 2022 when the water level in the well dropped below the suspended logger. 

The first year of deployment from August 2016 to August 2017 may be considered suspect because the the data logger record cannot be strongly tied to any field readings. The logger was not deployed until a month after the well depth measurements were collected in July 2016. Additionally, the water table was noted as being 4 cm above the ground surface in July 2017, but no actual well depth measurements were collected during that visit or during the next visit in August 2017 to repair the well.

There is a gap from August 2017 to September 2018 because the logger was accidentally not set to record data during that deployment. There is another gap from early December 2020 to August 2022 when the logger malfunctioned and was either recording obviously incorrect data or no data at all. A new logger was deployed in August 2022 and is currently logging.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_YOSE-11_Well-322/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-322plot
#| fig-cap: "Water level record for well 322"
continuousWaterLevel(well = "322")
```

```{r}
#| label: tbl-322visits
#| tbl-cap: "Site visit data for well 322"
discreteVisitDataReactable(well = "322")
```

```{r}
#| label: tbl-322loggers
#| tbl-cap: "Logger deployment data for well 322"
loggerWellDeploymentsReactable(well = "322")
```

### Fen 323 (Porcupine Flat)

The record begins in August 2017 and is continuous through August 2024. There are periods in late summer and fall of 2018, 2019, 2020, 2021, and 2022 when the water level in the well dropped below the suspended logger. During the visit in early August 2023, there was a discrepancy of 15.5 cm between the arrival depth to water measurement and the departure depth to water measurement following repairs to the well, so there is some uncertainty for these field readings. The current logger has been deployed since August 2017. This logger may be nearing the end of its battery life and should be replaced during the next visit.

Continuous water level data are also available to view and download from the [Aquarius Web Portal](https://irma.nps.gov/aqwebportal/Data/DataSet/Chart/Location/SIEN_WEI_YOSE-11_Well-323/DataSet/Water%20Level/BaroCompensated/Interval/AllData).

```{r}
#| label: fig-323plot
#| fig-cap: "Water level record for well 323"
continuousWaterLevel(well = "323")
```

```{r}
#| label: tbl-323visits
#| tbl-cap: "Site visit data for well 323"
discreteVisitDataReactable(well = "323")
```

```{r}
#| label: tbl-323loggers
#| tbl-cap: "Logger deployment data for well 323"
loggerWellDeploymentsReactable(well = "323")
```
